### 2015-06-13 improv.tex
1/psi replacement

%!TEX root =  autocontgrlp.tex
\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
\begin{align}
||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
\end{proof}

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
\begin{lemma}\label{gshiftmn}
Let $J_1\in \R^n$ and $k\in \R$ be a constant. If $J_2=J_1+k\psi$, then $\Gamma J_2\leq \Gamma J_1+\beta_{\psi} k\psi$.
\end{lemma}
\begin{proof}
The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
\end{proof}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in weighted $L_\infty$ with factor $\beta_{\psi}$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\infty,1/\psi}$. Thus
\begin{align}\label{ineq}
J_2-\epsilon\psi\leq J_1\leq J_2+\epsilon \psi.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshiftmn}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\beta_{\psi} \epsilon\psi\leq \Gamma J_1\leq \Gamma J_2+\beta_{\psi} \epsilon\psi.
\end{align}
Thus
\begin{align}
||\Gamma J_1-\Gamma J_2||_{\infty,1/\psi}\leq \beta_{\psi} ||J_1-J_2||_{\infty,1/\psi}.
\end{align}
\end{proof}
\begin{corollary}\label{hgmaxcontramn}
$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
\end{corollary}
\begin{proof}
Follows from arguments similar to Theorem~\ref{gmaxcontramn}.
\end{proof}
\begin{lemma}\label{cmt1mn}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
\begin{align}
||J^*-\hv||_{\infty,1/\psi}\leq \frac{2||J^*-\Phi r^*||_{\infty,1/\psi}+||\Gamma J^*-\hg J^*||_{\infty,1/\psi}}{1-\beta_{\psi}}.
\end{align}
\end{lemma}
\begin{proof}
The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\infty,1/\psi}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
\end{proof}

We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}
\begin{lemma}\label{restate}
Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ , $r \in \R^k$ be an arbitrary vector and let $r'$ be such that
\begin{align}
\Phi r'=\Phi r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, \psi.
\end{align}
Then $r'$ is feasible for the ALP in \eqref{alp}. 
\end{lemma}
\begin{theorem}\label{mt2mn}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
\begin{align}
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}
%\nn\\&
+||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_{\infty,1/\psi}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}
||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.\nn
\end{align}
Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\infty,1/\psi}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\infty,1/\psi}+||J^*-\hv||_{\infty,1/\psi}).
\end{align}
The result follows from Corollary~\ref{cmt1}.\\
\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
\end{proof}
\begin{theorem}\label{cmt2mn}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
\end{align}
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
\end{proof}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}$, then 
\begin{align}
||J^*-\bj||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\mn} \psi\geq TJ^*$.
\end{proof}

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
\begin{lemma}\label{gshiftmn}
Let $J_1\in \R^n$ and $k\in \R$ be a constant. If $J_2=J_1+k\psi$, then $\Gamma J_2\leq \Gamma J_1+\beta_{\psi} k\psi$.
\end{lemma}
\begin{proof}
The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
\end{proof}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in weighted $L_\infty$ with factor $\beta_{\psi}$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\mn}$. Thus
\begin{align}\label{ineq}
J_2-\epsilon\psi\leq J_1\leq J_2+\epsilon \psi.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshiftmn}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\beta_{\psi} \epsilon\psi\leq \Gamma J_1\leq \Gamma J_2+\beta_{\psi} \epsilon\psi.
\end{align}
Thus
\begin{align}
||\Gamma J_1-\Gamma J_2||_{\mn}\leq \beta_{\psi} ||J_1-J_2||_{\mn}.
\end{align}
\end{proof}
\begin{corollary}\label{hgmaxcontramn}
$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
\end{corollary}
\begin{proof}
Follows from arguments similar to Theorem~\ref{gmaxcontramn}.
\end{proof}
\begin{lemma}\label{cmt1mn}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\mn}$ then
\begin{align}
||J^*-\hv||_{\mn}\leq \frac{2||J^*-\Phi r^*||_{\mn}+||\Gamma J^*-\hg J^*||_{\mn}}{1-\beta_{\psi}}.
\end{align}
\end{lemma}
\begin{proof}
The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\mn}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
\end{proof}

We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}
\begin{lemma}\label{restate}
Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ , $r \in \R^k$ be an arbitrary vector and let $r'$ be such that
\begin{align}
\Phi r'=\Phi r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, \psi.
\end{align}
Then $r'$ is feasible for the ALP in \eqref{alp}. 
\end{lemma}
\begin{theorem}\label{mt2mn}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\mn}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\mn}$, then
\begin{align}
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}
%\nn\\&
+||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_{\mn}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}
||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.\nn
\end{align}
Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
\end{align}
The result follows from Corollary~\ref{cmt1}.\\
\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
\end{proof}
\begin{theorem}\label{cmt2mn}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
\end{align}
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
\end{proof}

### 2015-06-13 lp.tex
1/psi replacement

We let $\R_+$ denote the set of nonnegative reals. \todoc{Move up?}
For any function $\chi\colon S\ra \R_+$, define the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as
\begin{align*}
\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}\,.
\end{align*}
\begin{definition}
A function $\chi:S\to\R_+$ is said to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ 
	if $\beta_{\chi}<1$.
\end{definition}
The error bound will be given in terms of a Lyapunov function $\psi$ for $P$ that is in the column span of $\Phi$:
\begin{assumption}\label{lyap}
$\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$.
\end{assumption}
It is straightforward to check that the vector $\one$ when viewed as a $S \to \R_+$ function 
is a Lyapunov function. 
Further, by \cref{one}, $\one$ is trivially present in the column span of $\Phi$, 
hence, \cref{lyap} is not limiting.

%In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states. A higher value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
With this, we can recall the said result.  %below  which bounds the error in the approximate value function.
\begin{theorem}[Theorem~$4.2$ of \cite{ALP}]
\label{restateval}
Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be as in \cref{lyap} 
and $c$ be a distribution as in \eqref{probdist}. Then, it holds that
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}\,.
\end{align*}
\end{theorem}
The next result  the loss in performance of a policy that is greedy w.r.t. $J_{\tu}$:
\begin{theorem}[Theorem~$3.1$ of \cite{ALP}]
\label{restatepol}
Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
\begin{align*}
||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'}\,,
\end{align*}
where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.
\end{theorem}
Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
Note that the ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
\todoc{Column generation, Dantzig-Wolf decomposition?}

>>>>

We let $\R_+$ denote the set of nonnegative reals. \todoc{Move up?}
For any function $\chi\colon S\ra \R_+$, define the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as
\begin{align*}
\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}\,.
\end{align*}
\begin{definition}
A function $\chi:S\to\R_+$ is said to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ 
	if $\beta_{\chi}<1$.
\end{definition}
The error bound will be given in terms of a Lyapunov function $\psi$ for $P$ that is in the column span of $\Phi$:
\begin{assumption}\label{lyap}
$\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$.
\end{assumption}
It is straightforward to check that the vector $\one$ when viewed as an $S \to \R_+$ function 
is a Lyapunov function. 
Further, by \cref{one}, $\one$ is trivially present in the column span of $\Phi$, 
hence, \cref{lyap} is not limiting.
In what follows we will always assume that Assumptions \ref{probdist}--\ref{lyap} hold.

%In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states. A higher value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
With this, we can recall the said result.  %below  which bounds the error in the approximate value function.
\begin{theorem}[Theorem~$4.2$ of \cite{ALP}]
\label{restateval}
Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$.
% $\psi$ be as in \cref{lyap} 
%and $c$ be a distribution as in \eqref{probdist}. 
Then, it holds that
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}\,.
\end{align*}
\end{theorem}
The next result  the loss in performance of a policy that is greedy w.r.t. $J_{\tu}$:
\begin{theorem}[Theorem~$3.1$ of \cite{ALP}]
\label{restatepol}
Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP. Then,
\begin{align*}
||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'}\,,
\end{align*}
where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.
\end{theorem}
Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
Note that the ALP is a linear program in $k$ ($\ll n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
\todoc{Column generation, Dantzig-Wolf decomposition?}

### 2015-06-13 polbnd.tex
1/psi replacement

\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
We now bound the performance of the greedy policy $\hu$.
\begin{theorem}\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function. Let $r^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{polthebnd}
||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}\big).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}\label{polderv}
||J_{\hu}-\hj||_{1,c}&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
&\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},
\end{align}
where in the second inequality, for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. Now
\begin{align}
||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.
\end{align}
The result now follows by substituting the value of $||J^*- \hj||_{\mn}$ from Corollary~\ref{cmt2mn}.
\end{proof}
\begin{note}
By letting $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}+||J^*-\hg J^*||_{\mn}$ (inequality follows from Lemma~\ref{bestbndmn}), we can also modifiy the bounds in \eqref{finalbnd} and \eqref{polthe} as
\begin{align}
\label{loose1}||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}).\\
\label{loose2}||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}\big).
\end{align}
Here the term $||J^*-\hg J^*||$ in \eqref{loose1} and \eqref{loose2} captures the error due to the use of both $\Phi$ and $W$. Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the aim here is to capture the error due to function approximation as well as constraint reduction in a single term.
\end{note}

>>>>

%!TEX root =  autocontgrlp.tex
\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
We now bound the performance of the greedy policy $\hu$.
\begin{theorem}\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function. Let $r^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{polthebnd}
||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}\big).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}\label{polderv}
||J_{\hu}-\hj||_{1,c}&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
&\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},
\end{align}
where in the second inequality, for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. Now
\begin{align}
||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.
\end{align}
The result now follows by substituting the value of $||J^*- \hj||_{\mn}$ from Corollary~\ref{cmt2mn}.
\end{proof}
\begin{note}
By letting $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ (inequality follows from Lemma~\ref{bestbndmn}), we can also modifiy the bounds in \eqref{finalbnd} and \eqref{polthe} as
\begin{align}
\label{loose1}||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}).\\
\label{loose2}||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}\big).
\end{align}
Here the term $||J^*-\hg J^*||$ in \eqref{loose1} and \eqref{loose2} captures the error due to the use of both $\Phi$ and $W$. Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the aim here is to capture the error due to function approximation as well as constraint reduction in a single term.
\end{note}
